---
title: "Master CHA1-3 Combined"
date: "2024-06-20"
output:
  html_document:
    theme: cerulean
    toc: yes
    toc_float:
      collapsed: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
This setup is commonly used at the beginning of an R Markdown document to configure global settings for code chunks, ensuring consistent behavior throughout the document.

```{r message=FALSE, warning=FALSE}
install.packages(c("rvest", "httr", "stringr"))
install.packages("RSelenium")
install.packages("webdriver")
install.packages("chromedriver")

library(tidyverse)
library(rio)
library(janitor)
library(dplyr)
library(rvest) 
library(httr) 
library(stringr)
library(RSelenium)

```
CHA 1 data (money to vendors is skewed bc flawed data (Hap to Owner column of 2021Q2), so avoided using after initial memo):
```{r}
CHA_2020_4 <- rio::import("https://github.com/wellsdata/DJNF_Merrill/raw/main/data/CHA_Data_24_053R.xlsx", sheet = "2020Q4") %>% 
  mutate(quarter="2020Q4") %>% 
  clean_names()

CHA_2021_1 <- rio::import("https://github.com/wellsdata/DJNF_Merrill/raw/main/data/CHA_Data_24_053R.xlsx", sheet = "2021Q1") %>% 
  mutate(quarter="2021Q1") %>% 
  clean_names()

CHA_2021_2 <- rio::import("https://github.com/wellsdata/DJNF_Merrill/raw/main/data/CHA_Data_24_053R.xlsx", sheet = "2021Q2") %>% 
  mutate(quarter="2021Q2") %>% 
  clean_names()

CHA_2021_3 <- rio::import("https://github.com/wellsdata/DJNF_Merrill/raw/main/data/CHA_Data_24_053R.xlsx", sheet = "2021Q3") %>% 
  mutate(quarter="2021Q3") %>% 
  clean_names() %>% 
  rename(vendor_id = vendor_i)

CHA_2021_4 <- rio::import("https://github.com/wellsdata/DJNF_Merrill/raw/main/data/CHA_Data_24_053R.xlsx", sheet = "2021Q4") %>% 
  mutate(quarter="2021Q4") %>% 
  clean_names() %>% 
  rename(vendor_id = vendor_i)

CHA_2022_1 <- rio::import("https://github.com/wellsdata/DJNF_Merrill/raw/main/data/CHA_Data_24_053R.xlsx", sheet = "2022Q1") %>% 
  mutate(quarter="2022Q1") %>% 
  clean_names() %>% 
  rename(vendor_id = vendor_i)

CHA_2022_2 <- rio::import("https://github.com/wellsdata/DJNF_Merrill/raw/main/data/CHA_Data_24_053R.xlsx", sheet = "2022Q2") %>% 
  mutate(quarter="2022Q2") %>% 
  clean_names() %>% 
  rename(vendor_id = vendor_i)

CHA_2022_3 <- rio::import("https://github.com/wellsdata/DJNF_Merrill/raw/main/data/CHA_Data_24_053R.xlsx", sheet = "2022Q3") %>% 
  mutate(quarter="2022Q3") %>% 
  clean_names() %>% 
  rename(vendor_id = vendor_i)

CHA_2022_4 <- rio::import("https://github.com/wellsdata/DJNF_Merrill/raw/main/data/CHA_Data_24_053R.xlsx", sheet = "2022Q4") %>% 
  mutate(quarter="2022Q4") %>% 
  clean_names() %>% 
  rename(vendor_id = vendor_i)

CHA_2023_1 <- rio::import("https://github.com/wellsdata/DJNF_Merrill/raw/main/data/CHA_Data_24_053R.xlsx", sheet = "2023Q1") %>% 
  mutate(quarter="2023Q1") %>% 
  clean_names() %>% 
  rename(vendor_id = vendor_i)

CHA_2023_2 <- rio::import("https://github.com/wellsdata/DJNF_Merrill/raw/main/data/CHA_Data_24_053R.xlsx", sheet = "2023Q2") %>% 
  mutate(quarter="2023Q2") %>% 
  clean_names() %>% 
  rename(vendor_id = vendor_i)

CHA_2023_3 <- rio::import("https://github.com/wellsdata/DJNF_Merrill/raw/main/data/CHA_Data_24_053R.xlsx", sheet = "2023Q3") %>% 
  mutate(quarter="2023Q3") %>% 
  clean_names() %>% 
  rename(vendor_id = vendor_i)

CHA_2023_4 <- rio::import("https://github.com/wellsdata/DJNF_Merrill/raw/main/data/CHA_Data_24_053R.xlsx", sheet = "2023Q4") %>% 
  mutate(quarter="2023Q4") %>% 
  clean_names() 
```

```{r}

CHA1 <- rbind(CHA_2020_4, CHA_2021_1, CHA_2021_2, CHA_2021_3, CHA_2021_4, CHA_2022_1, CHA_2022_2, CHA_2022_3, CHA_2022_4, CHA_2023_1, CHA_2023_2, CHA_2023_3, CHA_2023_4)

write.csv(CHA1,"CHA1.csv")
```
CHA2 data
```{r}

CHA2_2019 <- import("CHA2(Jan2019-April2024).xlsx", sheet = "2019") %>% 
  mutate(year="2019") %>% 
  clean_names()

CHA2_2020 <- import("CHA2(Jan2019-April2024).xlsx", sheet = "2020") %>% 
  mutate(year="2020") %>% 
  clean_names()

CHA2_2021 <- import("CHA2(Jan2019-April2024).xlsx", sheet = "2021") %>% 
  mutate(year="2021") %>% 
  clean_names()

CHA2_2022 <- import("CHA2(Jan2019-April2024).xlsx", sheet = "2022") %>% 
  mutate(year="2022") %>% 
  clean_names()

CHA2_2023 <- import("CHA2(Jan2019-April2024).xlsx", sheet = "2023") %>% 
  mutate(year="2023") %>% 
  clean_names()

CHA2_2024 <- import("CHA2(Jan2019-April2024).xlsx", sheet = "2024 April") %>% 
  mutate(year="2024") %>% 
  clean_names()

CHA2 <- rbind(CHA2_2019, CHA2_2020, CHA2_2021, CHA2_2022, CHA2_2023, CHA2_2024)

CHA2$vendor_zip <- as.numeric(CHA2$vendor_zip)
CHA2$payment_month_number <- as.numeric(CHA2$payment_month_number)
CHA2$bedroom_size <- as.numeric(CHA2$bedroom_size)

write.csv(CHA2,"CHA2.csv")

colnames(CHA2)

summary(CHA2$vendor_address_line_1)

CHA2 %>% 
  count(vendor_address_line_1) %>% 
  arrange(desc(n)) %>% 
  head(10) 

#because there are multiple entries per month (grrrr), going to have to go with total payment amount to find any valuable data analysis 

sum(CHA2$payment_amount, na.rm = TRUE)
# [1] 2,867,739,566
mean(CHA2$payment_amount, na.rm = TRUE)
# 845.3352

vendors <- CHA2 %>% 
  select(vendor_name, vendor_address_line_1, payment_amount, year, zip) %>% 
  group_by(vendor_address_line_1) %>% 
  summarize(
    # vendor_name,
    # year,
    # zip,
    Total_Payment = sum(payment_amount, na.rm=TRUE), 
    Mean_Payment = mean(payment_amount, na.rm=TRUE),
    
    ) %>%  
  arrange(desc(Total_Payment))

#how much money each vendor receives from the CHA per year (yearly breakdown to find patterns over time)
vendors_year <- CHA2 %>% 
  select(vendor_name, vendor_address_line_1, payment_amount, year, zip) %>% 
  group_by(vendor_address_line_1, year) %>% 
  summarize(
    # vendor_name,
    # year,
    # zip,
    Total_Payment = sum(payment_amount, na.rm=TRUE), 
    Mean_Payment = mean(payment_amount, na.rm=TRUE),
    
    ) %>%  
  arrange(desc(Total_Payment))

# leases_per_owner <- CHA2 %>% 
#   count(vendor_name) %>% 
#   arrange(n) 

#Top vendors paid by CHA by vendor id 
vendors_by_id <- CHA2 %>% 
  select(vendor_name, vendor_address_line_1, payment_amount, year, zip, vendor_id) %>% 
  group_by(vendor_id) %>% 
  summarize(
    # vendor_name,
    # year,
    # zip,
    Total_Payment = sum(payment_amount, na.rm=TRUE), 
    Mean_Payment = mean(payment_amount, na.rm=TRUE),
    ) %>%  
  arrange(desc(Total_Payment))

top_vendors_based_on_id <- CHA2 %>% 
  filter(vendor_id %in% c("v0019379", "v0040721", "v0003121", "vp002409", "v0034028", "v0042878", "v0038810", "v0027505")) %>% 
  select(vendor_name, vendor_id) %>% 
  mutate(
    Vendor = case_when(
      vendor_id == "v0019379" ~ "Top_Vendor",
      vendor_id == "v0040721" ~ "Second_Vendor",
      vendor_id == "v0003121" ~ "Third_Vendor",
      vendor_id == "vp002409" ~ "Fourth_Vendor",
      vendor_id == "v0034028" ~ "Fifth_Vendor",
      vendor_id == "v0042878" ~ "Sixth_Vendor",
      vendor_id == "v0038810" ~ "Seventh_Vendor",
      vendor_id == "v0027505" ~ "Eighth_Vendor"
    )
  ) %>%
  group_by(Vendor) %>% 
  summarize(vendor_names = paste(unique(vendor_name), collapse = ", ")) %>% 
  pivot_wider(names_from = Vendor, values_from = vendor_names)
  
# atlas <- CHA2 %>% 
#   select(vendor_id, address, payment_amount, year) %>% 
#   filter(!vendor_id=="v0040721") %>% 
#   filter(!address=="S Colfax Ave") %>% 
#   group_by(vendor_id) %>%
#   summarise(
#     # vendor_name,
#     # year,
#     # zip,
#     Total_Payment = sum(payment_amount, na.rm=TRUE),
#     Vendor = vendor_id
#     ) %>%  
#   arrange(desc(Total_Payment))

icarus <- CHA2 %>% 
  select(vendor_id, year, payment_amount) %>%
  filter(vendor_id =="v0034886") %>% 
  group_by(vendor_id, year) %>% 
  summarize(
    Total_Payment = sum(payment_amount, na.rm=TRUE)
  ) %>% 
  arrange(desc(Total_Payment))
  
atlas <- CHA2 %>% 
  select(vendor_id, year, payment_amount) %>%
  filter(vendor_id =="v0040721") %>% 
  group_by(vendor_id, year) %>% 
  summarize(
    Total_Payment = sum(payment_amount, na.rm=TRUE)
  ) %>% 
  arrange(desc(Total_Payment))

vendor_names_by_top_address <- CHA2 %>% 
  select(vendor_address_line_1, vendor_name) %>% 
  filter(vendor_address_line_1 %in% 
           c("C/O WPD MANAGEMENT LLC", "5454 S SHORE DR", "549 W RANDOLPH ST FL 2", "9252 N KILBOURN AVE", "329 W 18TH ST", "1 N LA SALLE ST STE 400", "3706 W MONTROSE AVE", "1020 W MONTROSE AVE", "1912 S STATE ST", "1131 WEST WARNER RD STE 102", "150 W MAPLE ST, OFFICE", "350 W HUBBARD ST STE 500", "C/O BRINSHORE DEVELOPMENT LLC", "3115 W AUGUSTA BLVD", "2101 S MICHIGAN AVE")
    ) %>% 
  group_by(vendor_address_line_1) %>% 
  summarize(
    Vendor = paste(unique(vendor_name))
  )


```

Zip codes extracted from CHA2 dataset

```{r}
# zip_list <- CHA2 %>% 
#   select(year, zip)%>% 
#   group_by(zip) 
# 
# CHA2 %>% 
#   count(zip) %>% 
#   arrange(n)

zip_list_per_year <- CHA2 %>% 
  mutate(zip = substr(zip, 1, 6)) %>%  # Extract first 6 digits of the zip code
  group_by(year, zip) %>%              # Group by year and the modified zip code
  summarise(count = n())               # Count occurrences

zip_list <- CHA2 %>% 
  mutate(zip = substr(zip, 1, 5)) %>%  # Extract first 5 digits of the zip code
  group_by(zip) %>%              # Group by the modified zip code
  summarise(count = n())

# # List of 86 ZIP codes from CHA2
# zip_codes <- c("60014", "60026", "60050", "60077", "60085", "60098", "60104",
#                "60155", "60201", "60302", "60409", "60411", "60419", "60422",
#                "60425", "60426", "60428", "60429", "60432", "60438", "60445",
#                "60458", "60465", "60471", "60473", "60478", "60601", "60602",
#                "60603", "60605", "60606", "60607", "60608", "60609", "60610",
#                "60611", "60612", "60613", "60614", "60615", "60616", "60617",
#                "60618", "60619", "60620", "60621", "60622", "60623", "60624",
#                "60625", "60626", "60628", "60629", "60630", "60631", "60632",
#                "60633", "60634", "60636", "60637", "60638", "60639", "60640",
#                "60641", "60642", "60643", "60644", "60645", "60646", "60647",
#                "60649", "60651", "60652", "60653", "60654", "60655", "60656",
#                "60657", "60659", "60660", "60661", "60707", "60803", "60805",
#                "60827")
#The Amount calculated per zip code is skewed because uneven amount of months per property and even entries per month (going to need to use CHA1 if need to find zip code breakdown per amount but will also need to limit the time frame for data)
```

Census Tract HUV zip code data, filtered for the 86 zip codes from CHA2.

```{r}
Census_Zip_2019 <- import("Zipcode_2019 HCV Census .xlsx") %>% 
  clean_names()  

Census_Zip_2020 <- import("Zipcode_2020 HCV Census .xlsx") %>% 
  clean_names()

Census_Zip_2021 <- import("Zipcode_2021 HCV Census .xlsx") %>% 
  clean_names()

Census_Zip_2022 <- import("Zipcode_2022 HCV Census.xlsx") %>% 
  clean_names()

Census_Zip_2023 <- import("Zipcode_2023 HCV Census.xlsx") %>% 
  clean_names()

Census_Zip <- rbind(Census_Zip_2019, Census_Zip_2020, Census_Zip_2021, Census_Zip_2022, Census_Zip_2023) %>% 
  filter(program_label == "Housing Choice Vouchers") %>% 
  rename(zip_codes = entities) %>% 
  rename(date = quarter) %>% 
  select(date, zip_codes, program_label, total_units, people_per_unit, rent_per_month, spending_per_month, hh_income, pct_disabled_all, pct_age62plus, pct_minority)
 
#Filter for the 86 zip codes --> analyze the census data

Census_Zip$zip_codes <- as.character(Census_Zip$zip_codes)

zip_codes_to_filter <- c("60014", "60026", "60050", "60077", "60085", "60098", 
                         "60104", "60155", "60201", "60302", "60409", "60411", 
                         "60419", "60422", "60425", "60426", "60428", "60429", 
                         "60432", "60438", "60445", "60458", "60465", "60471", 
                         "60473", "60478", "60601", "60602", "60603", "60605", 
                         "60606", "60607", "60608", "60609", "60610", "60611", 
                         "60612", "60613", "60614", "60615", "60616", "60617", 
                         "60618", "60619", "60620", "60621", "60622", "60623", 
                         "60624", "60625", "60626", "60628", "60629", "60630", 
                         "60631", "60632", "60633", "60634", "60636", "60637", 
                         "60638", "60639", "60640", "60641", "60642", "60643", 
                         "60644", "60645", "60646", "60647", "60649", "60651", 
                         "60652", "60653", "60654", "60655", "60656", "60657", 
                         "60659", "60660", "60661", "60707", "60803", "60805", 
                         "60827")

#data is a breakdown per year per zip (5 zips because 5 years)
Census_CHA_Zip <- Census_Zip %>%
  filter(zip_codes %in% zip_codes_to_filter) %>% 
  select(date, zip_codes, program_label, total_units, people_per_unit, rent_per_month, spending_per_month, hh_income, pct_disabled_all, pct_age62plus, pct_minority)

#Total census data per zip code from 2019 to 2023
Census_CHA_Zip_Total <- Census_CHA_Zip %>% 
  group_by(zip_codes) %>% 
  summarize(
    Total_Units = sum(total_units, na.rm=TRUE), 
    People_per_Unit = mean(people_per_unit, na.rm=TRUE),
    Rent_per_month = mean(rent_per_month, na.rm=TRUE),
    Spending_per_Month = mean(spending_per_month, na.rm=TRUE),
    HH_Income = mean(hh_income, na.rm=TRUE),
    Pct_Disabled_All = mean(pct_disabled_all, na.rm=TRUE),
    Pct_Age62Plus = mean(pct_age62plus, na.rm=TRUE),
    Pct_Minority = mean(pct_minority, na.rm=TRUE)
    
    )
  
summary(Census_CHA_Zip_Total)

```


```{r}





```


